Face Attractiveness and the Sense of Reality

### 2022-09-09 analysis.Rmd

# Introduction

The goal of this study was to...

@@

```{r message=FALSE, warning=FALSE}
outliers <- c(
  # Very short duration for questionnaire in particular + low rating correlations
  "5eaef8702b68455d6e130595_ptsga"
  )
outliers_partial <- c(
  "5c6414540821d30001046198_x9q7r",
  "60dd7b03f1e72d38230df476_9yh9n")
```

@@

@@

```{r message=FALSE, warning=FALSE}
data.frame(Participant = c("Total"), t(sapply(dfsub[2:ncol(dfsub)], mean, na.rm = TRUE))) |>
  rbind(dfsub) |>
  mutate(Attention_Check = paste0(
    insight::format_value(Attention_Check, 1),
    " (", insight::format_value(Attention_Check1, 1),
    ", ",
    insight::format_value(Attention_Check2, 1),
    ", ",
    insight::format_value(Attention_Check3, 1),
    ")"
  )) |>
  select(-Attention_Check1, -Attention_Check2, -Attention_Check3) |>
  datawizard::data_relocate("Attention_Check", 2) |>
  knitr::kable() |>
  kableExtra::row_spec(1, italic = TRUE) |>
  kableExtra::row_spec(which(dfsub$Participant %in% outliers) + 1, background = "#EF9A9A") |> 
  kableExtra::row_spec(which(dfsub$Participant %in% outliers_partial) + 1, background = "#FFCC80")
```

@@

df |>
  ggplot(aes(x = Delay, y = Real)) +
  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
  geom_hline(yintercept = 0.5, linetype = "dotted") +
  # geom_ribbon(data=y_conf, aes(y=Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.3) +
  geom_line(data=y_conf, aes(y=Predicted, group=Belief), linetype = "dashed") +
  geom_ribbon(data=pred, aes(y=Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.3) +
  geom_line(data=pred, aes(y=Predicted), color="red") +
  scale_fill_gradientn(colors = c("white", "#795548"), guide = "none") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  theme_modern() +
  labs(title = "Effect of Re-exposure Delay", x = "Minutes") +
  theme(
    aspect.ratio = 1,
    strip.background = element_blank(),
    strip.placement = "outside",
    plot.title = element_text(face = "bold", hjust = 0.5)
  ) +
  ggside::geom_xsidedensity(fill = "#795548", color = "white") +
  ggside::geom_ysidedensity(fill = "#9C27B0", color = "white") +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  ggside::ggside(collapse = "all")
```

@@

    scale_color_manual(values=c("Male" = "#2196F3", "Female" = "#E91E63")) +
    scale_fill_manual(values=c("Male" = "#2196F3", "Female" = "#E91E63")) +
    scale_x_continuous(expand = c(0, 0), labels = scales::percent) +
    scale_y_continuous(expand = c(0, 0), labels = scales::percent) +
    theme_modern(axis.title.space=0) + 
    ggside::geom_xsidedensity(fill = fill, color = "white") +
    ggside::geom_ysidedensity(fill = "#9C27B0", color = "white") +
    ggside::theme_ggside_void() +
    ggside::scale_ysidex_continuous(expand = c(0, 0)) +
    ggside::scale_xsidey_continuous(expand = c(0, 0))

  list(p=p)
}
```

```{r message=FALSE, warning=FALSE}
rez_at <- make_model(filter(df, Stimulus_Interest == TRUE), 
                     formula = "poly(Attractive, 2) * Sex + Trustworthy + (1|Participant) + (1|Stimulus)", 
                     var="Attractive", fill = "#F44336")
rez_gl <- make_model(filter(df, Stimulus_Interest == TRUE), 
                     formula = "poly(Goodlooking, 2) * Sex + Trustworthy + (1|Participant) + (1|Stimulus)", 
                     var="Goodlooking", fill = "#E91E63")
rez_tr <- make_model(filter(df, Stimulus_Interest == TRUE), 
                     formula = "poly(Trustworthy, 2) * Sex + Goodlooking + (1|Participant) + (1|Stimulus)", 
                     var="Trustworthy", fill = "#4CAF50")
rez_fa <- make_model(filter(df, Stimulus_Interest == TRUE), 
                     formula = "poly(Familiar, 2) * Sex + (1|Participant) + (1|Stimulus)", 
                     var="Familiar", fill = "#2196F3")

@@

df$Self_Attractiveness <- rowMeans(df[c("SelfAttractiveness1", "SelfAttractiveness2")])

```

@@

efa <- parameters::factor_analysis(select(dfsub, starts_with("AI")), n=3, rotation="varimax", sort=TRUE)

dfsub <- predict(efa, names = c("AI_Enthusiasm", "AI_Realness", "AI_Danger")) |> 
  cbind(dfsub)
```
```{r message=FALSE, warning=FALSE}
r <- make_correlation(dfsub[sr], select(dfsub, AI_Enthusiasm, AI_Realness, AI_Danger))
filter(r, BF > 1)
```

>>>>

@@

```{r message=FALSE, warning=FALSE}
outliers <- c(
  # Very short duration for questionnaire in particular + low rating correlations
  "5eaef8702b68455d6e130595_ptsga"
  )
outliers_partial <- c(
  "5dc3485219ca0326027ce91f_37ho9",
  "5c6414540821d30001046198_x9q7r",
  "60dd7b03f1e72d38230df476_9yh9n")
```

@@

### Extreme Items

```{r message=FALSE, warning=FALSE}
extreme_items <- df |> 
  group_by(Stimulus, Belief) |>
  summarize(n = n() / nrow(dfsub)) |>
  pivot_wider(values_from = "n", names_from = "Belief") |> 
  mutate(File = paste0("experiment/stimuli/AMFD/", Stimulus)) |> 
  arrange(Real) |> 
  filter(Real < 0.2 | Real > 0.8)

p_item <- df |>
  filter(Stimulus %in% extreme_items$Stimulus) |> 
  mutate(Stimulus = fct_relevel(Stimulus, as.character(extreme_items$Stimulus))) |>
  ggplot(aes(x = Belief_Answer, y = Stimulus, fill = Stimulus)) +
  ggdist::stat_slab(scale = 2, slab_alpha = 0.9, normalize = "groups") +
  geom_vline(xintercept = 0, linetype = "dotted") +
  ggimage::geom_image(data=extreme_items, aes(image=File, x = 0, y=Stimulus), size=0.1, by="height") +
  # scale_y_discrete(expand = c(0.5, 0.5)) +
  scale_x_continuous(
    limits = c(-1, 1),
    expand = c(0, 0),
    breaks = c(-1, 0, 1),
    label = c("Fake", "", "Real")
  ) +
  scale_fill_viridis_d(option = "inferno") +
  labs(x = "Simulation Monitoring", y = "Participants", title = "Distribution of Reality Judgments") +
  guides(fill = "none") +
  see::theme_modern() +
  theme(
    # axis.text.y = element_blank(),
    plot.title = element_text(face = "bold", hjust = 0.5)
  )
# p_item

df <- df |> 
  filter(!Stimulus %in% extreme_items$Stimulus)
```

We removed `r nrow(extreme_items)` trials per participant.

@@

```{r message=FALSE, warning=FALSE}
data.frame(Participant = c(paste0("Total (n=", nrow(dfsub), ")")), t(sapply(dfsub[2:ncol(dfsub)], mean, na.rm = TRUE))) |>
  rbind(dfsub) |>
  mutate(Attention_Check = paste0(
    insight::format_value(Attention_Check, 1),
    " (", insight::format_value(Attention_Check1, 1),
    ", ",
    insight::format_value(Attention_Check2, 1),
    ", ",
    insight::format_value(Attention_Check3, 1),
    ")"
  )) |>
  select(-Attention_Check1, -Attention_Check2, -Attention_Check3) |>
  datawizard::data_relocate("Attention_Check", 2) |>
  knitr::kable() |>
  kableExtra::row_spec(1, italic = TRUE) |>
  kableExtra::row_spec(which(dfsub$Participant %in% outliers) + 1, background = "#EF9A9A") |> 
  kableExtra::row_spec(which(dfsub$Participant %in% outliers_partial) + 1, background = "#FFCC80")
```

@@

df |>
  ggplot(aes(x = Delay, y = Real)) +
  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
  geom_hline(yintercept = 0.5, linetype = "dotted") +
  # geom_ribbon(data=y_conf, aes(y=Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.3) +
  geom_line(data=y_conf, aes(y=Predicted, group=Belief), linetype = "dashed", color="red") +
  geom_ribbon(data=pred, aes(y=Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.3) +
  geom_line(data=pred, aes(y=Predicted), color="red") +
  scale_fill_gradientn(colors = c("white", "#795548"), guide = "none") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  theme_modern() +
  labs(title = "Effect of Re-exposure Delay", x = "Minutes") +
  theme(
    aspect.ratio = 1,
    strip.background = element_blank(),
    strip.placement = "outside",
    plot.title = element_text(face = "bold", hjust = 0.5)
  ) +
  ggside::geom_xsidedensity(fill = "#795548", color = "white") +
  ggside::geom_ysidedensity(fill = "#9C27B0", color = "white") +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  ggside::ggside(collapse = "all")
```

@@

    scale_color_manual(values=c("Male" = "#2196F3", "Female" = "#E91E63")) +
    scale_fill_manual(values=c("Male" = "#2196F3", "Female" = "#E91E63")) +
    scale_x_continuous(expand = c(0, 0), labels = scales::percent) +
    scale_y_continuous(expand = c(0, 0), labels = scales::percent) +
    theme_modern(axis.title.space=5) + 
    ggside::geom_xsidedensity(fill = fill, color = "white") +
    ggside::geom_ysidedensity(fill = "#9C27B0", color = "white") +
    ggside::theme_ggside_void() +
    ggside::scale_ysidex_continuous(expand = c(0, 0)) +
    ggside::scale_xsidey_continuous(expand = c(0, 0))

  list(p=p, model_belief=m_real)
}
```

```{r message=FALSE, warning=FALSE}
rez_at <- make_model(filter(df, Stimulus_Interest == TRUE), 
                     formula = "Sex / poly(Attractive, 2) + Trustworthy + (1|Participant) + (1|Stimulus)", 
                     var="Attractive", fill = "#F44336")
rez_gl <- make_model(filter(df, Stimulus_Interest == TRUE), 
                     formula = "Sex / poly(Goodlooking, 2) + Trustworthy + (1|Participant) + (1|Stimulus)", 
                     var="Goodlooking", fill = "#E91E63")
rez_tr <- make_model(filter(df, Stimulus_Interest == TRUE), 
                     formula = "Sex / poly(Trustworthy, 2) + Goodlooking + (1|Participant) + (1|Stimulus)", 
                     var="Trustworthy", fill = "#4CAF50")
rez_fa <- make_model(filter(df, Stimulus_Interest == TRUE), 
                     formula = "Sex / poly(Familiar, 2) + (1|Participant) + (1|Stimulus)", 
                     var="Familiar", fill = "#2196F3")

parameters::parameters(rez_at$model_belief)
parameters::parameters(rez_gl$model_belief)
parameters::parameters(rez_tr$model_belief)
parameters::parameters(rez_fa$model_belief)

@@

df$Self_Attractiveness <- rowMeans(df[c("SelfAttractiveness1", "SelfAttractiveness2")])
```

@@

efa <- parameters::factor_analysis(select(dfsub, starts_with("AI")), n=3, rotation="varimax", sort=TRUE)
efa
dfsub <- predict(efa, names = c("AI_Enthusiasm", "AI_Realness", "AI_Danger")) |> 
  cbind(dfsub)
```
```{r message=FALSE, warning=FALSE}
r <- make_correlation(dfsub[sr], select(dfsub, AI_Enthusiasm, AI_Realness, AI_Danger))
filter(r, BF > 1)
```

### Social Anxiety

```{r message=FALSE, warning=FALSE}
r <- make_correlation(dfsub[sr], select(dfsub, starts_with("Social_")))
filter(r, BF > 1)
```

### Intolerance to Uncertainty

```{r message=FALSE, warning=FALSE}
r <- make_correlation(dfsub[sr], select(dfsub, starts_with("IUS_")))
filter(r, BF > 1)
```

### Narcissism

```{r message=FALSE, warning=FALSE}
r <- make_correlation(dfsub[sr], select(dfsub, starts_with("FFNI_")))
filter(r, BF > 1)
```

### Paranoid Beliefs

```{r message=FALSE, warning=FALSE}
r <- make_correlation(dfsub[sr], select(dfsub, starts_with("GPTS_")))
filter(r, BF > 1)
```
